\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\title{SportHub User Manual}
\author{Team 4}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Introduction}

\subsection{What is SportHub?}
SportHub is a web application that lets users view upcoming games for
multiple sports and keep a personal list of \textbf{favorite teams}.
From those favorite teams, SportHub builds a personalized list of
upcoming games. The main users are sports fans who want one place to
quickly see schedules and focus on the teams they care about most.

This manual explains:
\begin{itemize}
  \item The goals of SportHub and why the software matters.
  \item How to access SportHub from GitHub / Docker.
  \item How to navigate the main pages and use key features.
\end{itemize}

\subsection{Who is this manual for?}
This manual is intended for:
\begin{itemize}
  \item Sports fans using SportHub to view games and favorite teams.
  \item The CS3338 instructor and TAs who need to run and test the system.
  \item Team members and future developers who want a quick guide to the UI.
\end{itemize}

\section{Objectives of SportHub}

The main objectives of SportHub are:
\begin{itemize}
  \item Show a list of upcoming (and recent) games for different sports
        (NBA, NFL, Soccer, MLB, etc.).
  \item Allow the user to filter games by sport and date.
  \item Allow the user to mark \textbf{teams} as favorites and show a
        \textbf{My Favorites} view with upcoming games involving those teams.
  \item Provide a simple admin view so project members can add or edit
        teams and games without touching the database directly.
\end{itemize}

\section{Why this software matters}

Many sports fans jump between different apps and websites to check schedules
for different leagues. SportHub aims to collect multiple sports into a single
view and let users focus on the games that matter most to them by following
favorite teams. This reduces the time spent switching between sites and makes
it easier to track all favorite matchups in one place.

\section{Accessing SportHub}

\subsection{Requirements}

\subsubsection*{For end users}
\begin{itemize}
  \item Modern web browser (Chrome, Firefox, Edge, Safari).
  \item Stable internet connection (if running against a hosted instance).
\end{itemize}

\subsubsection*{For local development}
\begin{itemize}
  \item Git installed.
  \item Docker and Docker Compose (e.g., Docker Desktop).
  \item Optionally Node.js and npm (if running frontend/backend without Docker).
\end{itemize}

\subsection{GitHub Repository}

The source code and documentation are stored in GitHub:

\begin{itemize}
  \item GitHub: \url{https://github.com/uchiha1121/cs3338-final-sportapp}
\end{itemize}

\subsection{Jira Link}

Project tasks, sprint planning, and bugs are tracked using Jira:

\begin{itemize}
  \item Jira board:
        \url{https://calstatela-team4.atlassian.net/jira/software/projects/ST/boards/68?sprintStarted=true}
\end{itemize}

\subsection{How to run the project with Docker}

To run SportHub locally using Docker:

\begin{enumerate}
  \item Clone the GitHub repository:
        \begin{verbatim}
git clone https://github.com/uchiha1121/cs3338-final-sportapp.git
cd cs3338-final-sportapp
        \end{verbatim}
  \item Make sure Docker Desktop (or Docker engine) is running.
  \item Start all services with Docker Compose:
        \begin{verbatim}
docker-compose up --build
        \end{verbatim}
  \item After the containers start, open a browser and go to:
        \begin{quote}
          \texttt{http://localhost:3000}
        \end{quote}
        or the port configured for the frontend in \texttt{docker-compose.yml}.
\end{enumerate}

To stop the application, press \texttt{Ctrl + C} in the terminal where
\texttt{docker-compose} is running, then optionally run:

\begin{verbatim}
docker-compose down
\end{verbatim}

\section{Navigation Overview}

\subsection{Top navigation bar}

All pages share a top navigation bar with links such as:

\begin{itemize}
  \item \textbf{SportHub} -- logo or text that returns to the Home page.
  \item \textbf{All Games} -- view all upcoming games with filters.
  \item \textbf{Teams} -- browse teams and select favorites.
  \item \textbf{My Favorites} -- view upcoming games involving favorite teams
        (shown only when logged in).
  \item \textbf{Admin} -- admin tools for managing teams and games
        (shown only for admin users).
  \item \textbf{Login / Logout} -- sign in or sign out.
\end{itemize}

\subsection{Main pages}

The main pages of SportHub are:
\begin{itemize}
  \item \textbf{Home} -- landing page that introduces SportHub and links to
        All Games, Teams, and My Favorites.
  \item \textbf{All Games} -- list of games with filters for sport and date.
  \item \textbf{Teams} -- list of teams by sport with favorite controls.
  \item \textbf{My Favorites} -- personalized schedule of games for favorite teams.
  \item \textbf{Admin} -- screens for managing teams and games (admin only).
  \item \textbf{Login / Register} -- authentication pages for users.
\end{itemize}

\section{Using SportHub}

\subsection{Home Page}

When you first open SportHub, you typically see the Home page.

\begin{itemize}
  \item Read the short description of what the app does.
  \item Use buttons or links on this page to go to All Games, Teams, or
        My Favorites.
\end{itemize}

\subsection{Viewing Games (All Games Page)}

\begin{enumerate}
  \item Click \textbf{All Games} in the navigation bar.
  \item Use the \textbf{sport filter} (e.g., All, NBA, NFL, Soccer, MLB) to choose
        the sport you care about.
  \item Use the \textbf{date filter} or date picker (if provided) to select a day.
  \item Browse the list of games:
        \begin{itemize}
          \item Each entry shows sport, home team, away team, date, time, and status.
          \item Click the \textbf{Details} button or link (if available) to
                open the Game Details page.
        \end{itemize}
\end{enumerate}

If no games match your filters, SportHub shows a message like
``No games available for this selection.''

\subsection{Browsing Teams and Adding Favorites (Teams Page)}

\begin{enumerate}
  \item Click \textbf{Teams} in the navigation bar.
  \item Use the sport filter or tabs to narrow the list to a specific league.
  \item Look through the list of teams and find the ones you care about.
  \item If you are logged in, click the \textbf{favorite star or toggle}
        on a team card to mark it as a favorite.
  \item Click the favorite control again to remove a team from favorites.
\end{enumerate}

If you are not logged in, SportHub may show a message like
``Log in to save favorite teams'' when you try to use the favorite button.

\subsection{Viewing Favorite Teams and Games (My Favorites Page)}

\begin{enumerate}
  \item Make sure you are logged in (see Section~\ref{subsec:login}).
  \item Click \textbf{My Favorites} in the navigation bar.
  \item At the top, you may see a summary of your favorite teams.
  \item Below, you will see upcoming games that involve any of your favorite teams.
  \item If you no longer want to follow a team, use the unfavorite control on
        the Teams page or from any favorite summary (if available).
\end{enumerate}

If you have no favorite teams, SportHub shows a message like:
``You have no favorite teams yet. Go to the Teams page to add some.''

\subsection{Game Details Page}

When you click a specific game on the All Games or My Favorites page, the
Game Details page opens.

\begin{itemize}
  \item You will see a header showing the two teams and the league/sport.
  \item Details include game date, time, location, and status.
  \item If scores are recorded, they may be shown as home and away scores;
        otherwise, the score fields may show ``TBD'' or be blank.
  \item Use the back button or navigation links to return to the previous page.
\end{itemize}

\subsection{Logging In and Registering}
\label{subsec:login}

\subsubsection*{Registering an Account}
\begin{enumerate}
  \item Click \textbf{Register} (or a sign-up link near the Login form).
  \item Enter your email/username and password (and confirm the password, if required).
  \item Submit the form.
  \item If the registration is successful, you may be redirected to the Login page
        or logged in automatically, depending on the implementation.
\end{enumerate}

\subsubsection*{Logging In}
\begin{enumerate}
  \item Click \textbf{Login} in the navigation bar.
  \item Enter your email/username and password.
  \item Click the \textbf{Login} button.
  \item On success, the navigation bar should update (for example, showing
        My Favorites and Logout).
\end{enumerate}

If your credentials are invalid, you should see an error message. Double-check
your information and try again.

\subsection{Admin Features (Admin Page)}

If your user account has admin permissions, you will see an
\textbf{Admin} link in the navigation bar.

\begin{itemize}
  \item Click \textbf{Admin} to access admin tools.
  \item Use the Teams management section to add, edit, or delete teams.
  \item Use the Games management section to add, edit, or delete games.
  \item Always click \textbf{Save} or \textbf{Update} to apply changes.
\end{itemize}

These tools are primarily for project developers or the instructor and
are not required for normal fan usage.

\section{Troubleshooting}

\subsection*{The site does not load}
\begin{itemize}
  \item Make sure Docker containers are running (if using Docker).
  \item Check that you are using the correct URL (e.g., \texttt{http://localhost:3000}).
  \item Try refreshing the browser or using a different browser.
\end{itemize}

\subsection*{No games are showing}
\begin{itemize}
  \item Check the filters on the All Games page (sport and date).
  \item If running locally, verify that the database has been seeded with teams and games.
\end{itemize}

\subsection*{I cannot favorite teams}
\begin{itemize}
  \item Make sure you are logged in.
  \item If the favorite button is disabled or shows an error, check for any
        on-screen message explaining the issue.
\end{itemize}

\subsection*{I forgot my password}
\begin{itemize}
  \item In this class project version, a full password reset system may not be implemented.
  \item Contact the project team or reset the database if necessary.
\end{itemize}

\section{Support and Contact}

If you need help with SportHub or find a bug:

\begin{itemize}
  \item Check the GitHub README for setup updates:
        \url{https://github.com/uchiha1121/cs3338-final-sportapp}
  \item Create an issue in the GitHub repository.
  \item Talk to the CS3338 instructor or a team member during class or lab time.
\end{itemize}

\end{document}
