\section*{Snapshot 3 -- Checkpoint 2}

\subsection*{Objective}

The main objective for Snapshot 3 is to add a Favorites feature to
SportHub so that fan users can mark interesting games and then see them
on a dedicated ``My Favorites'' page. This snapshot focuses on basic
frontend behavior and planning the backend support, not on a full
production database implementation.

\subsection*{Planned Work}

For Snapshot 3 we plan to:

\begin{itemize}
  \item Extend the All Games page so each game has a ``Favorite'' icon
        or button the user can click.
  \item Create a simple ``My Favorites'' page that lists only the games
        the current user has marked as favorites.
  \item Store favorites on the frontend (for example, using browser
        storage or an in-memory list) while we design the real backend
        API and database tables.
  \item Add new Jira stories and tasks for the Favorites feature,
        including UI, backend design, and test work.
  \item Create new TestRail test cases and a Snapshot 3 report that
        cover marking a game as favorite, viewing favorites, and
        removing a game from favorites.
  \item Update the SRS, SDD, Design Spec, and User Manual to describe
        the Favorites feature and the My Favorites page.
  \item Update the workflow diagram to show the flow for adding and
        viewing favorites.
\end{itemize}

\subsection*{Completed Work (by the end of Snapshot 3)}

By the end of Snapshot 3 we expect to have:

\begin{itemize}
  \item A working prototype of the Favorites button on the All Games
        page that visually marks games as favorited.
  \item A simple My Favorites page that shows the subset of games the
        user has favorited (even if this is based on mock data or
        temporary frontend storage).
  \item New Jira issues created and updated for the Favorites feature,
        including at least one story and several tasks.
  \item A TestRail run and PDF report for Snapshot 3 that documents
        manual tests for the Favorites workflow.
  \item All major documents (SRS, SDD, Design Spec, User Manual)
        updated with short sections describing how Favorites should
        work in the final system.
\end{itemize}

\subsection*{Next Steps After Snapshot 3}

After Snapshot 3 the next steps will be:

\begin{itemize}
  \item Connect the Favorites feature to a real backend API and
        database tables so favorites persist across browser sessions.
  \item Add basic authentication so favorites can be tied to a specific
        logged-in user account.
  \item Improve the UI/UX of the My Favorites page (sorting, filtering,
        removing favorites).
  \item Expand TestRail coverage for error handling and edge cases and
        prepare the final Snapshot 4 deliverables and reflection.
\end{itemize}

