\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Snapshot 4 – Final Objective}

For Snapshot 4 (original due date), our goal is to finish SportHub,
clean up the project, and reflect on future work.
This snapshot bundles three areas: feature polish, validation (TestRail/Jira),
and documentation alignment (SRS, SDD, user manual, design spec, workflow).

\subsection*{Goals}
\begin{itemize}
  \item Polish the UI for all pages (games list, favorites, admin).
  \item Complete admin tools for adding, editing, or removing games.
  \item Fix bugs found in TestRail and finalize all test runs.
  \item Update SDD, SRS, user manual, design spec, and workflow diagram
        to match the final implementation.
  \item Add a reflection section describing what was completed,
        what could not be finished, and ideas for future work
        (more sports, live score APIs, authentication, etc.).
  \item Make sure the Docker setup runs the full system and the README
        explains how to start the app.
\end{itemize}

\subsection*{Completed for Snapshot 4}
\begin{itemize}
  \item Final TestRail run: added ``Snapshot 4 wrap up'' suite with C50--C53
        (All Games filter, Favorite toggle, My Favorites view, Admin CRUD) and
        executed regression across Snapshot 2 and 3 suites.
  \item Jira close-out: finalized sprint items (ST-21, ST-22, ST-23) covering
        regression, frontend polish, and workflow updates; backlog items for
        Favorites and All Games are closed or archived.
  \item Documentation refreshed: SRS/SDD updated for the final scope, design
        spec and user manual aligned to Favorites + admin CRUD, workflow notes
        updated for Snapshot 4 run steps and Docker usage.
  \item Frontend polish: fixed mock data syntax error, confirmed filters and
        Favorites interactions for the demo build.
\end{itemize}

\subsection*{Future Work (Post–Snapshot 4)}
\begin{itemize}
  \item Integrate a live sports data API (e.g., NBA/NFL/Soccer) and move off
        seeded data; add cron/queue for refreshing schedules.
  \item Add real authentication and persistence for favorites (DB-backed) plus
        role-based admin access.
  \item Notifications/alerts for upcoming games of favorite teams (email/web
        push) and simple box-score details on the Game Details page.
  \item CI/CD hardening: automated tests in pipeline, lint/format, and Docker
        image publishing to a registry.
\end{itemize}

\subsection*{Reflection}
\begin{itemize}
  \item What went well: the multi-sport view, favorites UX, and Docker setup
        delivered a consistent demo; documentation stayed current each snapshot.
  \item What slipped: persistent favorites, live data APIs, and richer admin UX
        were deferred for time; testing remained mostly manual via TestRail.
  \item Risks mitigated: clarified future work and kept backlog visible in Jira;
        included TestRail evidence (cases C50--C53) for the final run.
\end{itemize}

\end{document}
