\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Design Specification -- SportHub}

\section{Overview}
SportHub is a web application that lets users view upcoming games for
multiple sports and keep a personal list of \textbf{favorite teams}.
From those favorite teams, SportHub builds a personalized list of
upcoming games. This document describes the planned screens, main UI
elements, and shared components of the system.

The goal of this design specification is to give a clear breakdown of
\textbf{every page and major part} of the SportHub user interface so
that developers can implement it consistently and the instructor can
see how the project is organized.

\section{Global Layout}
All pages share a consistent layout:

\begin{itemize}
  \item A top navigation bar with links:
        \textbf{SportHub} (Home), \textbf{All Games}, \textbf{Teams},
        \textbf{My Favorites} (for logged-in users), and
        \textbf{Admin} (for admin users).
  \item A main content area in the center of the page where each view
        displays its specific content.
  \item A footer with basic information about the team, course, and
        a brief note about the project.
  \item A consistent color theme and typography across all pages.
\end{itemize}

\section{Home Page}
\subsection*{Purpose}
Serve as the landing page for SportHub and give users a quick overview
of what the site does, along with shortcuts to the main features.

\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Page header} with the SportHub logo and tagline
        (for example, ``Multi-Sport Scores \& Favorites Tracker'').
  \item \textbf{Introductory text} briefly explaining that users can
        browse games, mark favorite teams, and view personalized
        schedules.
  \item \textbf{Quick links or cards} that navigate to:
        \begin{itemize}
          \item \textbf{All Games} -- browse all upcoming games.
          \item \textbf{Teams} -- choose favorite teams.
          \item \textbf{My Favorites} -- view games for favorite teams
                (visible only when logged in).
        \end{itemize}
  \item \textbf{Optional highlights}, such as a small list of games
        happening today or this week.
\end{itemize}

\section{All Games Page}
\subsection*{Purpose}
Show all upcoming games so the user can quickly see what is happening
across different sports.

\subsection*{Main Elements}
\begin{itemize}
\item \textbf{Filters area} at the top:
        \begin{itemize}
          \item Dropdown to select a sport (e.g., All, NBA, NFL, MLB,
                Soccer).
          \item Date picker or simple date filter
                (e.g., Today, This Week, Custom Date).
        \end{itemize}
  \item \textbf{Games list} in the main content area:
        \begin{itemize}
          \item Each row or card shows the sport, home team, away
                team, date, time, and game status (e.g., Upcoming,
                Final, In Progress).
          \item A \textbf{details button/link} that navigates to the
                Game Details page for that game.
          \item If desired, a small indicator when either team is one
                of the user's favorite teams.
        \end{itemize}
  \item \textbf{Empty state message} displayed when no games match the
        selected filters (for example, ``No games available for this
        date and sport.'').
\end{itemize}

\section{Teams Page}
\subsection*{Purpose}
Allow users to browse teams by sport and choose which teams to follow
as favorites.

\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Sport filter} at the top (tabs or dropdown) so users
        can pick a league such as NBA, NFL, Soccer, or MLB.
  \item \textbf{Team list or grid}:
        \begin{itemize}
          \item Each team card shows the team name, sport, and
                optionally a logo or city.
          \item For logged-in users, a \textbf{favorite star or toggle}
                to add or remove the team from their favorites.
          \item For guests (not logged in), the favorite control may
                be shown but disabled, with a small message such as
                ``Log in to save favorites.''
        \end{itemize}
  \item \textbf{Feedback messages} when a team is added to or removed
        from favorites.
\end{itemize}

\section{Game Details Page}
\subsection*{Purpose}
Show detailed information about a single game selected from the All
Games or My Favorites pages.

\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Game header} with the league/sport and
        \texttt{Home Team vs.\ Away Team}.
  \item \textbf{Details section} including:
        \begin{itemize}
          \item Game date and time.
          \item Location or venue.
          \item Status (Upcoming, Final, etc.).
          \item Scores if available (otherwise labels such as
                ``TBD'' or ``--'').
        \end{itemize}
\item \textbf{Navigation controls}:
        \begin{itemize}
          \item A back button or link to return to the previous list.
          \item Optional quick links back to All Games or My Favorites.
        \end{itemize}
\end{itemize}

\section{My Favorites Page}
\subsection*{Purpose}
Allow the user to focus only on games involving the teams they care
about most.

\subsection*{Main Elements}
\begin{itemize}
  \item Page title: \textbf{My Favorites}.
  \item Short description explaining that this page shows upcoming
        games for the user's favorite teams.
  \item \textbf{Favorite teams summary} (optional) at the top,
        listing the names and sports of the teams the user follows.
  \item \textbf{Upcoming games list} that uses the same layout as the
        All Games page but filtered to only games involving favorite
        teams.
  \item \textbf{Unfavorite controls} so the user can remove a team
        from their favorites, which will eventually remove its games
        from the list.
  \item When the user has no favorite teams, an \textbf{empty state
        message}, such as ``You have no favorite teams yet. Go to the
        Teams page to add some.''
\end{itemize}

\section{Login Page}
\subsection*{Purpose}
Allow existing users to sign in and access personalized features such
as My Favorites.

\subsection*{Main Elements}
\begin{itemize}
  \item Page title: \textbf{Login}.
  \item \textbf{Form fields}:
        \begin{itemize}
          \item Email or username input.
          \item Password input.
        \end{itemize}
  \item \textbf{Buttons and links}:
        \begin{itemize}
          \item Login/Submit button.
          \item Link to the Register page for new users.
        \end{itemize}
  \item \textbf{Error and success messages}:
        \begin{itemize}
          \item Clear messages for invalid credentials or missing
                fields.
        \end{itemize}
\end{itemize}

\section{Register Page}
\subsection*{Purpose}
Allow new users to create a SportHub account so they can maintain a
list of favorite teams and personalize their experience.

\subsection*{Main Elements}
\begin{itemize}
  \item Page title: \textbf{Register} or \textbf{Create Account}.
  \item \textbf{Form fields}:
        \begin{itemize}
          \item Email or username.
          \item Password.
          \item Confirm password.
        \end{itemize}
  \item \textbf{Buttons and links}:
        \begin{itemize}
          \item Register/Sign Up button.
          \item Link back to the Login page.
        \end{itemize}
  \item \textbf{Validation messages}:
        \begin{itemize}
          \item Password mismatch errors.
          \item Missing required field warnings.
        \end{itemize}
\end{itemize}

\section{Admin Pages}
\subsection*{Purpose}
Give authorized project members (admins) a way to manage teams and
games without directly editing the database.

\subsection*{Admin -- Teams Management}
\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Teams table} listing existing teams with columns such
        as team name, sport, and status (active/inactive).
  \item \textbf{Actions} for each row:
        \begin{itemize}
          \item Edit button to open a form for updating a team.
          \item Delete button (with confirmation) to remove a team.
        \end{itemize}
  \item \textbf{Add Team form} with fields:
        \begin{itemize}
          \item Team name.
          \item Sport (dropdown).
          \item Optional city/logo URL.
        \end{itemize}
  \item \textbf{Save} and \textbf{Cancel} buttons for the form.
\end{itemize}

\subsection*{Admin -- Games Management}
\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Games table} with columns such as sport, home team,
        away team, date, time, location, and status.
  \item \textbf{Actions} for each game:
        \begin{itemize}
          \item Edit button to update date, time, location, or status.
          \item Delete button (with confirmation) to remove the game.
        \end{itemize}
  \item \textbf{Add Game form} with fields:
        \begin{itemize}
          \item Sport.
          \item Home team (selected from existing teams).
          \item Away team (selected from existing teams).
          \item Date and time.
          \item Location.
          \item Optional status or score fields.
        \end{itemize}
  \item \textbf{Save} and \textbf{Cancel} buttons for the form.
\end{itemize}

\section{Shared Components and Tools}
\subsection*{Navigation Bar}
\begin{itemize}
  \item Always visible at the top of the page.
  \item Links:
        \begin{itemize}
          \item SportHub logo (navigates to Home).
          \item All Games.
          \item Teams.
          \item My Favorites (visible only for logged-in users).
          \item Admin (visible only for admin users).
          \item Login or Logout button depending on authentication state.
        \end{itemize}
\end{itemize}

\subsection*{Game Card Component}
\begin{itemize}
  \item Reusable layout used on All Games and My Favorites pages.
  \item Displays sport, teams, date/time, and game status.
  \item Contains a button or link to view full details.
  \item May show a small icon if the user follows one or both teams.
\end{itemize}

\subsection*{Team Card Component}
\begin{itemize}
  \item Used on the Teams page.
  \item Shows team name, sport, and optional logo/city.
  \item Provides a favorite star or toggle when the user is logged in.
\end{itemize}

\subsection*{Empty State Messages}
\begin{itemize}
  \item Standard messages for when lists have no content, such as:
        \begin{itemize}
          \item ``No games available for this selection.''
          \item ``You have no favorite teams yet.''
          \item ``No teams found for this sport.''
        \end{itemize}
  \item These help guide users toward the next step (e.g., going to the
        Teams page to add favorites).
\end{itemize}

\end{document}
