\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{longtable}

\title{TestRail Report -- Snapshot 4 Wrap Up}
\author{Team 4}
\date{2025-01-20}

\begin{document}

\maketitle

\section*{Overview}
Snapshot 4 focused on polishing All Games filters, finalizing the Favorites
experience, demonstrating a simple Admin CRUD flow, and closing out the sprint
with TestRail evidence (suite: ``Snapshot 4 wrap up''). All cases below were
executed on the seeded demo build (frontend + backend via \texttt{docker-compose}).

\section*{Test Cases Executed}
\begin{longtable}{|p{1.5cm}|p{10cm}|p{2cm}|}
\hline
\textbf{ID} & \textbf{Title / Notes} & \textbf{Result} \\
\hline
C50 & All Games filter: select NBA, list shows only NBA games; reset to All shows all sports. & Pass \\
\hline
C51 & Favorite toggle: clicking star on a game marks it favorite (star stays filled on reload) and adds to My Favorites. & Pass \\
\hline
C52 & My Favorites view: shows only favorited teams’ upcoming games; unfavoriting removes them from the view immediately. & Pass \\
\hline
C53 & Admin game CRUD (happy path): add a game with valid fields, edit date/time, delete it; list updates and no stale entries remain. & Pass \\
\hline
\end{longtable}

\section*{Regression Coverage}
Prior suites from Snapshot 2 (filters) and Snapshot 3 (favorites) were spot-checked
on the same build to ensure no regressions. No new defects were logged.

\section*{Environment}
\begin{itemize}
  \item Frontend: demo build served on port 3000 (seeded data).
  \item Backend: Express mock API on port 4000 via \texttt{docker-compose}.
  \item Data: seeded games list; favorites stored on frontend for demo.
\end{itemize}

\section*{Follow-Ups / Future Work}
\begin{itemize}
  \item Add automated test execution (CI) and backend-persisted favorites once auth/DB are enabled.
  \item Integrate live sports data API to replace seeded schedule.
  \item Expand admin coverage with validation/negative cases once persistence is in place.
\end{itemize}

\end{document}
